---
title: "DFIRE_RNA"
author: "TC"
date: "2018/04/12"
output:
  xaringan::moon_reader:
    css: ["default", "default-fonts"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---



```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE,echo=FALSE)
library(data.table)
library(dplyr)
library(tidyr)
library(ggplot2)
```


## Training dataset

- PDB RNA structures only (without protein or DNA)
- resolution < 3.0A.
- removed structures in decoy sets
- removed homologs using cd-hit-est (sequence identity < 0.8, sequence coverage 0.8)

---
## benchmarks

- decoy test
- near native ranking


---
## Decoy test

- 85 cases 


```{r fig.align='center', echo=FALSE,fig.height=5}
mydata <- data.frame(kb=c("DFIRE","3dRNAscore","RASP","KB","Rosetta"),Count = c(85,84,79,80,53))

gg <- ggplot(data=mydata,aes(x=kb,y=Count))+
  geom_col(aes(fill = kb))+
  geom_text(aes(label=Count))

print(gg)

```


    
---

## Near native test

- top 10% by score and top 10% by GDT_TS
- 43 cases, 500 decoys
- ES: 1~10, higher 

```{r fig.align='center', echo=FALSE,fig.height=5}
load("~/GIT/dfire_rna/dataset/ggplot_data.rda")
gg <- ggplot(data=ggplot_data,aes(x=type,y=ES))+
  geom_boxplot()

print(gg)

```



---
## Other work

- RMSD

- GDT_TS implementation? 

- other scores.



