---
title: "SPalign_RNA: SPalign for RNA Structures"
subtitle: "dihedral & dipolar term"
author: "TC"
date: "2018-08-08 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE, echo=FALSE}
options(htmltools.dir.version = FALSE, echo = FALSE)
```

class: center, middle, inverse

## SPalign_RNA

---
## Background
- Size independent structure similarity score

- SPscore: Use $L^{1-\alpha}$
    - may go beyond 1.0

$$SPs = \frac{1}{3.75*L^{1-\alpha}} * \sum_{d_{ij} < 2d_0}({\frac{1}{1+\frac{d_{ij}^2}{d_{0}^2}}} - 0.2)$$

$$\alpha = 0.3$$

--
- RMscore (similar to TMscore) : Use $d_0$

$$RMscore =\frac{1}{L} * \sum_{i = 1}^{L_{aln}}({\frac{1}{1+\frac{d_{i}^2}{d_{0}^2}}})$$

$$d_0 = max(\sqrt[3]{L_N -8.11} - 0.44, 0.25)$$

---

## SPscore distribution (seqid == 100)

```{r echo=FALSE, fig.align='center',fig.height=5}
load("~/GIT/spalign/SPalignNS/spalign_data/tmpdata/balance_fscor_gg3.rda")



gg3
```

---

## Fscor-balance: test dataset from RMalign (similar to TMscore)

--

- Derived from fscor(RNA functional classification)
- 901 positive/ 901 negative pairs 


--
- Cleaning:
  - 335 positive pairs have identical sequence(seqid = 100%), 
      - These may be easy cases to boost the performance
  - 10 duplicated pairs in negative pairs
  
  
  
---

## Result



```{r echo = FALSE}
load("~/GIT/spalign/SPalignNS/spalign_data/tmpdata/balance_fscor.rda")

rslt.df <- rslt.df[c(5,1,2,3,4),]

knitr::kable(rslt.df,digits = 3,format = "markdown") 
```

- highest mcc, acc, f1 are shown


**RMalign seems to perform better on this test**


---

## Result: Pairwise score comparison

```{r echo=FALSE, fig.align='center',fig.height=5}
load("~/GIT/spalign/SPalignNS/spalign_data/tmpdata/balance_fscor_gg.rda")

gg
```

- Solid: cutoff which maximize MCC
- Dash : RMscore cutoff reported in paper: 0.5

---

## Result: pairwise score(seqid == 100)

```{r echo=FALSE, fig.align='center',fig.height=5}
load("~/GIT/spalign/SPalignNS/spalign_data/tmpdata/balance_fscor_gg2.rda")

gg2
```

---

## Ongoing

- SPalign_RNA benchmarks

- DFIRE_RNA tweaks