---
title: "SPalign_RNA: SPalign for RNA Structures"
author: "TC"
date: "2018-09-25 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(tidyverse)
knitr::opts_chunk$set(
  echo = FALSE,
  fig.width = 7,
  fig.height = 5,
  fig.align = "center"
)
```

class: center, middle, inverse

## SPalign_RNA

---

## Comparison with RMalign

- Random RNA pairs
- pair_num: number of pairwise alignment performed
- nali: number of alignment length (mean)
- rmsd: root mean square deviation (mean)

```{r}
df <- read.csv("~/GIT/map_align/spalign_data/tmpdata/scor_seqid08_RM_SP.csv")

df <- df[,-1]

knitr::kable(df, format="html",digits = 3)
```



---
## Nali & RMSD

.pull-left[


```{r fig.cap="Nali, x:spalign, y:rmalign"}
load("~/GIT/map_align/spalign_data/tmpdata/rslt_rmsp.rda")
rslt_rmsp$gg1
```


]

.pull-right[
```{r fig.cap="RMSD, x:spalign, y:rmalign"}
rslt_rmsp$gg2
```

]

--
.foot-note[
RMSDs not ideal.
]

---

class: center, middle, inverse

## Alignment by map_align

---

## Method

- RNA contact map
    - RNA base distance < 8.0A

- map_align
    - Using default parameters
    - Total score = overlapping contacts - gap penalty 
    
- Test: Scor binary classification test

---

## Result - Scor binary classification test

```{r}
load("~/GIT/map_align/spalign_data/tmpdata/rslt.mapaln.rda")
```

```{r}
knitr::kable(rslt.mapaln$dfall,format="markdown",digits = 3)
```



```{r fig.height=4, fig.width=8}
rslt.mapaln$gg1
```

---

## ROC

```{r fig.width=11,fig.height=7}
rslt.mapaln$ggroc
```

---

## Score

```{r fig.width=11,fig.height=7}
rslt.mapaln$ggscore
```

--
- Many false positives?


---

## Other Normalization

.pull-left[
- Unnormalized: $S_{Norm0}$
    - $S_{Norm1}=\frac{S}{min(N_{contact1},N_{contact1})}$
    - $S_{Norm2}=S_{Norm1}min(\frac{N_{contact}}{L})$
    - $S_{Norm3}=\frac{S}{min(L_1,L_2)}$
    - $S_{Norm3}=\frac{S}{min(L_1,L_2)^{0.7}}$
    - $S_{Norm4}=\frac{S}{min(L_1,L_2)^{0.3}}$
    - rm : rmalign score
    - spe : spalign score
]
.pull-right[
```{r}
load("~/GIT/map_align/spalign_data/tmpdata/norm.rslt.rda")

knitr::kable(norm.rslt$df,format="markdown",digits = 3)
```
]

---

## ROC curve

```{r fig.width=9,fig.height=7}
norm.rslt$gg
```


---
## RNA Contact Map examples

```{r}
load("~/GIT/map_align/spalign_data/tmpdata/mymapgg.rda")
```

```{r message=FALSE}
library(gridExtra)

set.seed(123)
id <- sample(1:length(mymapgg),12)

grid.arrange(grobs=mymapgg[id],nrow=3)
```


---



## Notes

.pull-left[
```{r}
rslt.mapaln$ggcon1
```
]

.pull-right[
- Short RNAs 
    - low contacts 
    - Unable to generate meaningful contact-map align
- Longer RNAs (30~)
    - performance of map_align is still below spalign/mapalign
]



