---
title: "DFIRE_RNA: DFIRE energy for RNA structures"
author: "TC"
date: "2018-08-01 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo = FALSE, message= FALSE}

library(tidyverse)
library(ggrepel)

draw_decoy = function(df){
  gg.data <- df %>% 
  # filter(score %in% c("dfire_v","rasp", "rosetta", "3drnascore"))%>% 
  gather(key="topn",value = "counts",2:4) %>%
  mutate(topn = factor(topn,levels = c("top1","top5","top10")),
         score = factor(score, levels = c("score_rosetta", "score_rasp", "score_3drna", "score_dfire")))

tmp <- ggplot(gg.data) + geom_col(aes(x=score,y=counts,fill=topn,group = topn),position = "dodge") +
  labs(fill = "native in topN") +
  geom_text(aes(x=score,y=counts,label=counts, fill=topn,group= topn),position = position_dodge(width = 0.9))

  return(tmp)
}




```


```{r echo = FALSE}
load("~/GIT/dfire_rna2/tmpdata/rslt.rnapot.l.rda")

load("~/GIT/dfire_rna2/tmpdata/rslt.farna.l.rda")

load("~/GIT/dfire_rna2/tmpdata/rslt.rnapuzzle.l.rda")

load("~/GIT/dfire_rna2/tmpdata/rslt.farfar.l.rda")
```


## DFIRE RNA



---

## Results - identifying native structures


```{r warning= FALSE, echo = FALSE, message= FALSE, fig.align= "center", fig.width= 9}



g1=draw_decoy(rslt.rnapot.l$decoy)  + theme(legend.position="none")+ggtitle("rnapot")

g2=draw_decoy(rslt.farna.l$decoy)+ theme(legend.position="none")+ggtitle("farna")

g3=draw_decoy(rslt.farfar.l$decoy)+ theme(legend.position="bottom")+ggtitle("farfar")

g4=draw_decoy(rslt.rnapuzzle.l$decoytest)+ theme(legend.position="bottom")+ggtitle("RNA puzzles")

ggs=list(g1=g1,g2=g2,g3=g3,g4=g4)

do.call(gridExtra::grid.arrange, ggs)
```


---

```{r warning= FALSE, echo = FALSE, message= FALSE}
tbl.rnapot = left_join(rslt.rnapot.l$enrich,rslt.rnapot.l$near,)

tbl.rnapuzzle = left_join(rslt.rnapuzzle.l$enrich_median, rslt.rnapuzzle.l$nearrank_median)

```


## Results - Ranking near-native structures

### rnapot



```{r warning= FALSE, echo = FALSE, message= FALSE}
knitr::kable(tbl.rnapot, digits= 3, format="html")

```

- All scores performs reasonably well in rnapot benchmark

.footnote[
* top1,5,10: lowest RMSD to native in top1/5/10 best structures.
* Enrichment score: Intersection of top 10% lowest energy structures and top 10% near-native structures, range: 1~10
]


---

## Results - Ranking near-native structures

### RNA Puzzles
```{r warning= FALSE, echo = FALSE, message= FALSE}




knitr::kable(tbl.rnapuzzle, caption = "rna puzzles", digits= 3, format="html")


```

- DFIRE improves over other scores on RNA puzzle benchmark.

---

## RNA puzzles enrichment score

```{r warning= FALSE, echo = FALSE, message= FALSE}
load("~/GIT/dfire_rna2/tmpdata/tmp.df.rda")

knitr::kable(tmp.df, digits= 3, format="html")
```

---

## Ongoing

- DFIRE_rna finalize
    - data/program cleanup

- RNA SS prediction
