---
title: "Work Report: Extracting RNA evolution constrains using DCA"
author: "TC"
date: "2019-04-24 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    bibliography: zotero.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)

source("~/GIT/rna_ml/R/misc.R")
source("~/GIT/rna_ml/R/riboswitch_funcs.R")
source("~/GIT/rna_ml/R/initial_models.R")
```



## Background

```{r echo = FALSE}
load("~/GIT/rna_ml/rdata/test.l.mapped.entr")
load("~/GIT/rna_ml/rdata/test.l.wdca")
```

- RNA contact pairs are 'mostly' pairs

- x: distance, y: Direct information(DCA)

```{r fig.align='center', fig.height=5, fig.width=7}
  test.l.mapped.entr[[1]] %>% 
  mutate(rankdca = rank(-DCA), rankwmi = rank(-wMI), rankmi = rank(-MI)) %>%
   filter(dist < 20) %>%
  filter(entropy > 0.5) %>%
  filter(!is.na(dist)) %>%
  filter(abs(V1-V2) >= 5) %>%
  # filter(DCA > 0.5)
  ggplot(aes(x=dist,y=DCA))+geom_point(aes(color =pair > 0))
```


---

## Method

- dataset: 6 RNA riboswitches with 45~434 NTs

- Models
  - Direct Information(DI) from Direct Coupling Analysis(DCA)
    $$DI(X;Y) = \sum_{x,y} P_{XY}(x,y) \log{P_{XY}(x,y) \over P_X(x) P_Y(y)}$$
  - weighted DI ( $W(wcpair) = 1, W(notpair) = 0$ )
    $$wDI(X;Y) = \sum_{x,y} W*P_{XY}(x,y) \log{P_{XY}(x,y) \over P_X(x) P_Y(y)}$$
  - last report:
      - Mutual Information (MI between column X and Y:)
      - weighted Mutual Information
      - Shuffle_model

---

## Results 1

.pull-left[
```{r}
bench.metr4(test.l.wdca[[1]]) %>%
  select(-acc) %>%
  knitr::kable(digits = 3,format="markdown")
```
]

.pull-right[
```{r}
bench.roc(test.l.wdca[[1]])
```

]

---

## Results 1

.pull-left[
```{r}
bench.metr4(test.l.wdca[[1]]) %>%
  select(-acc) %>%
  knitr::kable(digits = 3,format="markdown")
```

- Sequence number: 110
]

.pull-right[
```{r}
bench.roc(test.l.wdca[[1]])
```

]

---

## Results 2

.pull-left[
```{r}
bench.metr4(test.l.wdca[[2]]) %>%
  select(-acc) %>%
  knitr::kable(digits = 3,format="markdown")
```

- Sequence number: 434
]

.pull-right[
```{r}
bench.roc(test.l.wdca[[2]])
```

]

---

## Results 3

.pull-left[
```{r}
bench.metr4(test.l.wdca[[3]]) %>%
  select(-acc) %>%
  knitr::kable(digits = 3,format="markdown")
```

- Sequence number: 134
]

.pull-right[
```{r}
bench.roc(test.l.wdca[[3]])
```

]

---

## Results 4

.pull-left[
```{r}
bench.metr4(test.l.wdca[[4]]) %>%
  select(-acc) %>%
  knitr::kable(digits = 3,format="markdown")
```

- Sequence number: 45
]

.pull-right[
```{r}
bench.roc(test.l.wdca[[4]])
```

]

---

## Results 5

.pull-left[
```{r}
bench.metr4(test.l.wdca[[5]]) %>%
  select(-acc) %>%
  knitr::kable(digits = 3,format="markdown")
```

- Sequence number: 156
]

.pull-right[
```{r}
bench.roc(test.l.wdca[[5]])
```

]

---

## Results 6

.pull-left[
```{r}
bench.metr4(test.l.wdca[[6]]) %>%
  select(-acc) %>%
  knitr::kable(digits = 3,format="markdown")
```

- Sequence number: 288
]

.pull-right[
```{r}
bench.roc(test.l.wdca[[6]])
```

]

---

## Summary

- wDCA seems to be performing well in identifying native pairs

---
## Ongoing

- Project 1, Improving DFIRE energy functions

- Project 2, RNA evolution couplings from MSA

- Thesis review milestone
