---
title: "Work Report: Evolutional couplings RNA"
author: "TC"
date: "2019-06-05"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE, cache= TRUE)
# library(tidyverse)

library(tidyverse)
library(ggrepel)
library(kableExtra)
library(png)
library(grid)
```

## Project

- Benchmark Contact contact predictions on RNA

---
## Data

- 51/99 RFAM families with structure
   - 34 families: no X-RAY
   - 14: mapping issues (sequence too long etc)
   
- SS/contact annotation: x3dna-dssr/calculated my self

- generateMSA: cmalign

---

## Methods

.pull-left[
1. Generate MSA for evolutionarily related RNAs
2. Generate Predictive models 
3. Infer model parameters
]

.pull-right[

- Mutual Information
- DCA
  - mfDCA
  - plmDCA
  - gplmDCA
  - GREMLIN
  - plmc
- Meta predictors (Next)
  - PconsC (Random forest PSICOV+plmDCA)
  - CCMpred
  - MetaPSICOV
  - MSAvolve 
]


---
## Results
Sensitivity 

```{r fig.width= 8, fig.height=5,fig.align='center'}
img <- readPNG("/home/tc/GIT/rna_ml/plots/p4.png")
 grid.raster(img)
```

---
## Results
Precision

```{r fig.width= 8, fig.height=5,fig.align='center'}
img <- readPNG("/home/tc/GIT/rna_ml/plots/p3.png")
 grid.raster(img)
```

---
## Results
Effective MSA size, Length


```{r fig.width= 8,fig.align='center'}
img <- readPNG("/home/tc/GIT/rna_ml/plots/p2.png")
 grid.raster(img)
```

---
## Results
Pairwise-comparison

```{r fig.width= 8, fig.height=5,fig.align='center'}
img <- readPNG("/home/tc/GIT/rna_ml/plots/p1.png")
 grid.raster(img)
```

gplmDCA, gremlin and plmDCA are better than mfDCA and plmc


