---
title: "Work Report: Evolutional couplings RNA"
author: "TC"
date: "2019-08-28"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE, cache= FALSE, fig.align="center", fig.height=5, fig.width=9)
library(dplyr)
```


## Background

- Goal: Automatic tool for RNA evolutional coupling 

- Procedure
    1. Query RNA
    
    1. Build RNA profile from homologs
        - RFAM 
        - **Not belong to existing RFAM**
    1. Evolutional coupling analysis

---
## Pipelines

.pull-left[
#### blastn+ infernal pipeline

1. input RNA sequence 
1. Blastn + nt database
1. Predicted Secondary structure(SS)
    1. __SPOT-RNA__ 
    1. __RNAfold__ 
1. cmbuild
1. cmsearch 
1. DCA 
]

.pull-right[
#### RFAM pipeline

1. input RNA sequence

1. cm

1. CMalign with RFAM family sequence

1. DCA

]

---
class: center, middle, inverse
## Results

---
## Comparison of the 3 pipelies

```{r fig.align='center'}
load("~/GIT/rna_ml/tmpdata/gg1.rda")

gg1
```

- RFAM > infernal
- GREMLIN > Others
- Ongoing: Need to fine tuning DCA parameters

---
## By Case

```{r}
load("~/GIT/rna_ml/tmpdata/gg2.rda")

gg2
```


---
## Comparison of SS prediction (DCA: TOP L/4) and spot-RNA and RNAfold

```{r}
load("~/GIT/rna_ml/tmpdata/tmp3.rda")

tmp3 %>% arrange(desc(mcc)) %>% knitr::kable(digits=2, format="markdown")
```




---
## SS prediction: SPOT-RNA predicts more basepairs

```{r }
appimg <- png::readPNG("/home/tc/GIT/rna_ml/plots/venn_allpair.png")
grid::grid.raster(appimg)

```

---
## By Case: basepair prediction of SPOT-RNA and GREMLIN(top L/4)

```{r}
load("~/GIT/rna_ml/tmpdata/ggl.rda")

plot(ggl)
```



