---
title: "Work Report: Evolutional couplings RNA"
author: "TC"
date: "2019-08-07"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE, cache= FALSE)
library(dplyr)
```

## Project

- Background: RFAM families

- Goal: A server that combines sequence profile building(MSAs) and RNA contact prediction (DCAs)

- Rationale
    - Currently there is no tool that combines both, for RNA.
    
    - RFAM's limitation for RNA with unknown family
    
---

## Method

.pull-left[
#### blastn+ infernal pipeline

1. input RNA sequence 

1. Blastn + nt database -> multiple sequence alignment (MSA) **1st MSA**

1. SPOT-RNA -> predicted Secondary structure(SS)

1. infernal(cmbuild) + 1st MSA + predicted SS  -> Covariance model(CM)

1. infernal(cmsearch) + CM + nt database -> **2nd MSA**

1. 2ndMSA + DCA methods

]

.pull-right[
#### RFAM pipeline

1. input RNA sequence (query) (with known RFAM family mapping)

1. infernal(cmalign) + prebuild CM + RFAM family sequence + query -> MSA

1. DCA methods + MSA 

]

---

### Analysis step

1. Mapping structure info 
    - Distance (nearest-atom distance < 8.0Å)
    - Basepairs (using x3dna-DSSR)
        - Canonical
        - Non-Canonical

1. Metrics
    - Overall: pull all pairs 
    - MCC, F1, Precision(TP/(TP+FP)), sensitivity(TP/(TP+FN)) at different cutoffs (1/10L, 1/4L, L)



---

## Data

Two RNA sequence dataset with known structure and known RFAM family

- 35 RNA sequences from RFAM (**RFAM35**)
    - 99 RFAM families has known PDB structures
    - selected:
        - X-Ray, Resolution < 3.0Å
        - RNA length between 32 ~ 300
    - Status
      - blastn + infernal pipeline (Jaswinder)
          - Sequence issues, need
      - rfam pipeline (TC) finished
      
- 37 RNA sequences as test set for SPOT-RNA (**TS37**)
    - with known RFAM family
    - not used in SPOT-RNA training, so SS prediction are not 
    - Status
      - blastn + infernal pipeline finished
      - rfam pipeline finished

---

## Results

#### RF35 overall

- Reported results are using top 0.35*L (max MCC)
- TRUE: all basepairs identified by DSSR

```{r echo = FALSE}
testit.rfam = data.table::fread(
"type	mcc	f1	precision	sensitivity
plmdca	0.56	0.56	0.64	0.49
gremlin	0.54	0.54	0.62	0.48
gplmdca	0.54	0.54	0.62	0.48
plmc	0.50	0.50	0.58	0.45
mfdca	0.23	0.23	0.26	0.21"
)

names(testit.rfam) = c("method","mcc","f1","prec", "sens")

testit.blast=data.table::fread(
"type	mcc	f1	precision	sensitivity
plmdca	0.57	0.56	0.69	0.48
gremlin	0.55	0.54	0.66	0.46
gplmdca	0.56	0.56	0.68	0.47
plmc	0.54	0.54	0.66	0.46
mfdca	0.32	0.32	0.38	0.27"
)


names(testit.blast) = c("method","mcc","f1","prec", "sens")


```


.pull-left[
RFAM pipeline

```{r}
testit.rfam %>%
  knitr::kable( format="markdown")
```


]

.pull-right[
Blastn+infernal pipeline 
```{r}
testit.blast %>%
  knitr::kable( format="markdown")
```
]
---
#### TS37 overall

- Reported results are using top 0.35*L (max MCC)
- TRUE: all basepairs identified by DSSR

```{r echo=FALSE}
tmpdf = data.table::fread(
"method mcc1 mcc2 f11 f12 prec1 prec2 sens1 sens2
plmc 0.61 0.63 0.61 0.63 0.72 0.74 0.53 0.54
plmdca 0.31 0.65 0.31 0.64 0.36 0.76 0.27 0.56
gremlin 0.59 0.62 0.59 0.61 0.69 0.72 0.51 0.53
gplmdca 0.31 0.64 0.31 0.64 0.37 0.75 0.27 0.55
mfdca 0.23 0.41 0.23 0.41 0.27 0.49 0.20 0.36
")

tmpdf.rfam = tmpdf[,c(1,2,4,6,8)]
names(tmpdf.rfam) = c("method","mcc","f1","prec", "sens")

tmpdf.blastn = tmpdf[,c(1,3,5,7,9)]
names(tmpdf.blastn) = c("method","mcc","f1","prec", "sens")
```

.pull-left[
RFAM pipeline

```{r}
tmpdf.rfam %>%
  knitr::kable( format="markdown")
```


]

.pull-right[
Blastn+infernal pipeline 
```{r}
tmpdf.blastn %>%
  knitr::kable( format="markdown")
```
]

* gplmDCA and plmdca were due to mapping errors, will update

---

## Issues

- Mapping between structure & sequence

In RNAs, there does not exist a database like SIFTS that provides residue level mapping between PDB residue id and sequences. So we have to do the mapping.

---

## Next

- Consolidate the data with Jaswinder(blastn pipeline data for RF35 and TS37)

- Methods/Results sections

- web server



