---
title: "Work Report: RNAcoup"
author: "TC"
date: "2019-09-18"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE, cache= FALSE, fig.align="center", fig.height=5, fig.width=9)
library(dplyr)
```

## Project 

- An Fully Automatic Method for Evolution-Coupling Analysis of RNA

- Highlight:
   - homologous RNA search by CM (predicted SS +sequence)
   - evolution-coupling analysis with DCA
   
---

## Materials and Methods I

#### RNAcoup
1. input RNA sequence 
1. Blastn -> homologous by sequence
1. Predicted Secondary structure(SS)
    1. ~~SPOT-RNA~~ (Training data issue, not used)
    1. __RNAfold__ 
1. cmbuild -> Covariance model
1. cmsearch
1. Evolution-Coupling analysis
    - Gremlin (Best in our test)
    - plmc (Cell, 2016)
    - mfDCA (NAR, 2015)


---
## Materials and Methods II

#### Dataset


<!-- Finally: -->

- set1: 35 RNAs with RNA family
   - RNAcoup profile -> DCA
   - RFAM sequence profile -> DCA
- set2: 35 RNAs not mapped to known RFAM families  (redo: select from PDB)
   - RNAcoup sequence profile -> DCA

---

## Performance evaluation 

- Basepair prediction
   - basepair types
     - Canonical (AU GC, GU)
     - Non-canonical (others)
   - metrics: precision, sensitivity, mcc, f1, aupr,
   
- Topology prediction
   - pseudo-knots
      - require both stems to be predicted.
   - stem precision

---
class: center, middle, inverse
## Results

---

### One third of RNA chains in PDB are not mapped to RFAM families

All 4281 RNA chains from PDB database, Run cmfind + 3016 RFAM family models:
   - 3182 mapped to RFAM 
   - 1099 not mapped
   
Removing redundancy by cd-hit-est with 80% sequence identity cutoff
   - 128 mapped
   - 152 not mapped

**That's why RNAcoup is necessary**

---

### Evolutional coupling predicts better RNA fold topology than base pairs


#### RF35, all pairs
```{r}
load("~/GIT/rna_ml/tmpdata/tmp3.rda")

tmp3.s = tmp3[c(1,3,4,7,8),]

tmp3.s %>% arrange(desc(mcc)) %>%
  knitr::kable(digits=2, format="markdown")
```

---
### Precision of stems prediction ( 198 Stems(length >=1) of RF35)



```{r}
load("~/GIT/rna_ml/tmpdata/ggstem.rda")

gg.stem
```




|type|predicted|total|
|:-|:-|:-|
|spotrna|163|198|
|rnafold|134|198|
|EC|143|198|


---

### EC can partially correct incorrectly predicted SS

```
>4ZNP_A ss by dssr
GGGAUACAGGACUGGCGGAUUAGUGGGAAACCACGUGGACUGUAUCCGAAAAAAAGCCGACCGCCUGGGCAUC
.((((((((..(.<<<<<....((((....))))..)..))))))))........(((..>>>>>..)))...
>SPOT-RNA
GGGAUACAGGACUGGCGGAUUAGUGGGAAACCACGUGGACUGUAUCCGAAAAAAAGCCGACCGCCUGGGCAUC
((((((((((((..........(((((..)))))..)))))))))))).....((((((.......)))))).
>RNAfold
GGGAUACAGGACUGGCGGAUUAGUGGGAAACCACGUGGACUGUAUCCGAAAAAAAGCCGACCGCCUGGGCAUC
.((((((((..(..........((((....))))..)..))))))))........(((.........)))... (-23.30)
>GREMLIN TOP L/25
GGGAUACAGGACUGGCGGAUUAGUGGGAAACCACGUGGACUGUAUCCGAAAAAAAGCCGACCGCCUGGGCAUC
.((((((((.....<..<...((((......)))){...))))))))........(....>..>.....).}.
```

---

## example 2
```
>3iqr_A ss by dssr
GGCUUAUCAAGAGAGGUGGAGGGACUGGCCCGAUGAAACCCGGCAACCAGAAAUGGUGCCAAUUCCUGCAGCGGAAACGUUGAAAGAUGAGCCG
((((((((....(.(((...(((.<.<<)))......))))(((..(((....))).)))...(>>.>(((((....)))))..))))))))).
>SPOT-RNA
GGCUUAUCAAGAGAGGUGGAGGGACUGGCCCGAUGAAACCCGGCAACCAGAAAUGGUGCCAAUUCCUGCAGCGGAAACGUUGAAAGAUGAGCCG
((((((((......(((((((((.....))))...))))).(((.(((((..)))))))).......(((((((..)))))))..)))))))).
>RNAfold
GGCUUAUCAAGAGAGGUGGAGGGACUGGCCCGAUGAAACCCGGCAACCAGAAAUGGUGCCAAUUCCUGCAGCGGAAACGUUGAAAGAUGAGCCG
((((((((......(((...(((.....)))......))).((((.(((....)))))))........(((((....)))))...)))))))). (-33.40)
>GREMLIN TOP L/25
GGCUUAUCAAGAGAGGUGGAGGGACUGGCCCGAUGAAACCCGGCAACCAGAAAUGGUGCCAAUUCCUGCAGCGGAAACGUUGAAAGAUGAGCCG
.((((..(....(.((((...(...<<<.)......)))))(.....((....))....)...(>>>.(((((....)))))..))..))))..
```








