---
title: "Work Report: RNAcoup"
author: "TC"
date: "2019-10-16"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE, cache= TRUE, fig.align="center", fig.height=5, fig.width=9)
library(dplyr)
library(ggplot2)
```

```{r}
load("~/GIT/rna_ml/rdata/tmp.workspace.rda")
```



## Project 

- An Fully Automatic Method for Evolution-Coupling Analysis of RNA

---
## Dataset
- 4528 PDB with RNA -> 4281 RNA chains
  - 3128 mapped to RFAM
     - 3.5 Å, length 32~500
     - cd-hit-east clusterring: 132 
     - 1 RNA for 1 RFAM family: 50
     - **set1**: 50
  - 1099 not mapped 
     - 3.5 Å, length 32~500
     - cd-hit-east clusterring: 129
     - **set2**: 129
     
---
## Methods

- Compare DCA methods on predicting secondary structure

- Compare RNA sequence profiles (using GREMLIN)
  - RFAM family sequences
  - blastn
  - blastn + RNAfold + infernal
  
- Compare set1(mapped to RFAM) and set2 (unmapped)

- neff effect

---
## Results

- Compare DCA methods on predicting secondary structure

- Compare RNA sequence profiles (using GREMLIN)
  - RFAM family sequences
  - blastn
  - blastn + RNAfold + infernal
  
- Compare set1(mapped to RFAM) and set2 (unmapped)

- neff effect


---

## Compare DCA methods on predicting secondary structure in set1

- 2002 base pairs of 50 RNA in set1

```{r}
bench.pulled_set1_rfa %>%
  arrange(desc(mcc)) %>%
  knitr::kable(digits=2, format="html")
```


---

## By case



```{r}
plot_mcc(rslt.set1.rfa)+ ggtitle("set1, MCC of GREMLIN-plmc")
```

- GREMLIN is better than plmc (p:0.03, paired-t test) and mfDCA(p-value: 1.1e-6, paired-t test)


---
## Compare different RNA sequence profiles (using GREMLIN)

```{r}
# 
# bench.pulled_set1_rfa
# 
# bench.pulled_set1_inf
# 
# bench.pulled_set2_inf


tmp = rbind(bench.pulled_set1_rfa[1,],
                    bench.pulled_set1_inf[1,],
                    bench.pulled_set1_blast[1,],
            bench.pulled_set2_inf[1,]) 

# rownames(tmp) = c("set1_rfam","set1_infernal","set1_blastn")

tmp %>% 
  mutate(model="gremlin",
         set = c("set1_rfam","set1_infernal","set1_blastn","set2_infernal")) %>%
  select(set,model, mcc,f1,sensitivity, precision) %>%
  knitr::kable(digits=2, format="html")
```

---
## By case

```{r}
tb.set1 %>%
  ggplot(aes(score_gremlin_rfa, score_gremlin_inf)) +
  geom_point()+ geom_abline()
```

- RNA coup is better than RFAM profile in 20 of 50 cases

---
## Tertiary contacts

```{r}
load("~/GIT/rna_ml/rdata/perf.tertiary.rda")

perf.tertiary %>%
  arrange(desc(mcc)) %>%
  knitr::kable(digits=2, format="html")
```


---
## PR curve

```{r}
load("~/GIT/rna_ml/rdata/aupr.rda")


source("~/GIT/rna_ml/R/Benchmarks.R")
library(PRROC)
# lapply(aupr,plot)
plot(aupr[[1]])
```


