---
title: "Work Report: RNAcoup"
author: "TC"
date: "2019-11-14"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE, cache= TRUE, fig.align="center", fig.height=5, fig.width=9)
library(dplyr)
library(ggplot2)


```


class: center, inverse, middle

> # Manuscript progress finished, will send after the group meeting.
> TC


---

# Some more results:

### Novel RNA families outside RFAM2?

.pull-left[
- In set2 (PDB RNAs not mapped to RFAM)

- 18 of 136 has neff > 100 (highest: 961), 13 of 18 has MCC > 0.6


]

.pull-right[

```{r fig.height=8}
load("~/GIT/rna_ml/rdata/gg.set2.rda")

gg.set2+ ggtitle("Set2(Non-RFAM)")+ geom_vline(xintercept=100,color="red")+
  geom_hline(yintercept=0.5,color="red")
```



]

---

# Next step

## - DCA + RNA SS prediction

### - higher-order DCA terms to improve non-basepair contact prediction

#### - Revisiting RNA puzzle targets using RNAcoup

##### - DFIRE-RNA?  

###### - SPalign-RNA?


