---
title: "Work Report: RNAcoup"
author: "TC"
date: "2019-12-12"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE, cache= TRUE, fig.align="center", fig.height=5, fig.width=9)
library(dplyr)
library(ggplot2)

load("~/tmp.rda")
```

## Data cleaning

- Data clean (again)
  - set1: 55, RFAM. RNAs per family <=2
  - set2: 117, not mapped, minimum basepair >=10

- MSA
  - RNAcoup
     - blastn + predicted SS +infernal -> CM
     - CM -> NT database -> MSA
  - RFAM 
     - family sequence, family cm -> MSA
  - Blastn
     - blastn + NT database -> MSA

- DCA
  - GREMLIN
  - plmc
  - mfDCA(apc)
  

---

## Overall performance

```{r fig1, fig.height=7}

myfig1= readRDS("~/GIT/rna_ml/rdata/fig1.rds")
 
# gg1_set1inf_box
myfig1

```

---

## Breakdown of basepair prediction


```{r breakbp, fig.cap= "A: Breakdown of basepairs ,  B: Breakdown of structures"}

load("~/GIT/rna_ml/rdata/row1.rda")
 
# gg1_set1inf_box
# myfig1
row1

```

Left to right: Canonical, Noncanonical, stem pairs, isolated canonical pairs, PK pairs



---

## Comparing predicted SS (RNAfold/GREMLIN top L/4)

```{r examplefig, fig.height=6, fig.cap="red: false positives,black:reference, blue: correctly predicted"}

exp = magick::image_read_pdf("~/GIT/rna_ml/tmpdata/ggexp.pdf")
# knitr::include_graphics("/img/ggexp.pdf")
# print(exp)
plot(exp)
```


---
## Tertiary contact prediction 

```{r}

load("~/GIT/rna_ml/rdata/ggtertiary.rda") 

ggtertiary
```


---

## Comparison of different MSA (RNAcoup/RFAM/Blastn)


```{r fig.cap="A,B: precision,sensitivity, C,D: Pairwise comparison of MCC of RFAM versus RNAcoup(C), of Blastn versus RNAcoup (D)"}
load("~/GIT/rna_ml/rdata/gg2_pipe.rda") 
 
# gg1_set1inf_box
# myfig1
gg2_pipe
```


---

## Comparison of Set1 and Set2 RNAs (neff/L > 1)



```{r}

myfig2= readRDS("~/GIT/rna_ml/rdata/gg2_set.rds") 
 
# gg1_set1inf_box 
myfig2
```










