---
title: "Workreport"
author: "TC"
date: "2020-01-22"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      chakra: "https://cdnjs.cloudflare.com/ajax/libs/remark/0.14.0/remark.min.js"
      beforeInit: "https://api.sparks-lab.org/js/sparkscloud.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE, cache= TRUE, fig.align="center", fig.height=5, fig.width=9)
load("~/GIT/rna_ml/rdata/gglist.rda")
```



---
class: center middle inverse 

## RNAcmap


---

## Predicted SS: SPOT-RNA vs RNAfold


```{r}
gglist$RNAcmap_predss_scatter
```



---

## Final predicted bp of RNAcmap: SPOT-RNA vs RNAfold


```{r}
gglist$RNAcmap_ss_scatter
```


---

## Strict filtering of SPOT-RNA training 


```{r}
gglist$RNAcmap_ss_scatter_five
```

---

## F1-score vs neff/L

Blue: SPOT-RNA improved over RNAfold

```{r}
gglist$haircut
```


---

## F1-score of RNAcmap and predicted SS

Blue: SPOT-RNA improved over RNAfold

```{r}
gglist$haircut2
```

---
class: center middle inverse 

## Webserver


---
## Structure

A centralized job management server based on Google cloud platform.

.center[
```{r echo=FALSE, fig.align='center'}

DiagrammeR::mermaid(
"graph TB
A(Servers on aspen) --- C(Cloud)

B(Servers on gowonda) --- C


C --- D(User1)
C --- E(User2)
C --- F(User3)
C --- G(User4)

", height= 300
)
```
]

Benefits

- Centralized task management
- Simpler server set up.


---

## Cloud server structure

- Server specs:
  - 1GB RAM, 1 Cpu, 500 GB storage
  - Cost: ~40 AUD/month
  

Endpoints at https://api.sparks-lab.org. Used to interact with the SQL database on the server.
- static files : Downloads, PDFs
-  /upload : user submit a task using the form.
-  /tasks : check tasks 
-  /tasks?method=RNAcmap&status=0 : check RNAcmap tasks with status "in the queue"
-  /tasks/2/update?status=1 : set the status of task 2 as "in process"
-  /tasks/2/delete : delete all files of task 2




---

## Use the servers

- User: Submit a job
- User: bookmark job page
- Servers on aspen: process a job, upload results to the cloud server
- User: check result & delete job files

---

## Track job status

<button onClick="checkqueue('https://api.sparks-lab.org/tasks')"> Check the Job Queue Status </button>
<button onClick="checkthisjob('https://api.sparks-lab.org/tasks?id=45')"> Check Job Status  </button>
<button onClick="checkqueue('https://api.sparks-lab.org/tasks')"> Check Queue Status </button>
<button onClick="checkmyjobs('https://api.sparks-lab.org/tasks?info=132.234.113.205')"> Check My Jobs </button>

<div id="queueinfo"></div>

---

## Main website

- https://sparks-lab.org

- A static website using Hugo, deployed on Netlify

- Benefits
    - Version control (Git/Github)
    - fast
    - Independent to the cloud server. ~~Don't put all eggs in one basket~~