---
title: "Workreport"
author: "TC"
date: "2020-01-22"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      chakra: "https://cdnjs.cloudflare.com/ajax/libs/remark/0.14.0/remark.min.js"
      # beforeInit: "https://api.sparks-lab.org/js/sparkscloud.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE, cache= TRUE, fig.align="center", fig.height=5, fig.width=9)


library(patchwork)
library(ggplot2)
# load("~/GIT/rna_ml/rdata/gglist.rda")
```

## RNAcmap post processing: Monte Carlo sampling

- Temperature 5 -> 1, *0.9, 5000 steps each
    - codaMC: 10 ->1, *0.9, 500,000 steps
    
- Potentials: 
    - From codaMC:
      - stems: -1 ~ -4 for RNA 4bp helical structures  (Turner, 2004)
      - local (i-j <3): +100
    - New:
      - lone-pair: +10
      - non-canonical: +0.5
      - RNAcmap contacts constraints: -10
    
- Initial SS: 
    - RNAcmap predicted SS

---
## Results1: F1 improved, precision ðŸ‘‡ ,sensitivity â˜

```{r}
load("/home/tc/GIT/RNA_SSMC/data/ggl.rda")



patch=
  ggl$f1+ labs(title="(A)",y="F1-score")+
  ggl$prec+labs(title="(B)",y="Precision")+
  ggl$sens+labs(title="(C)",y="Sensitivity") & theme(legend.position="bottom")

patch + plot_layout(guides="collect")
```


---
## Case levels

```{r}
load("/home/tc/GIT/RNA_SSMC/data/ggscatter.rda")



patch=
  ggscatter$mc2cmap+labs(title="(A) MC vs RNAcmap",y="F1-score")+
  ggscatter$mc2ss+labs(title="(B) MC vs predicted SS",y="F1-score") & theme(legend.position="bottom")

patch + plot_layout(guides="collect")
```

---
## Example

```{r}
load("/home/tc/GIT/RNA_SSMC/data/ggexp.rda")

# ggexp$mcdca
patch=
  ggexp$mcdca+labs(title="MC versus RNAcmap")+ theme(legend.position="bottom")+
  ggexp$ssref+labs(title="predicted SS versus Reference") & theme(legend.position="bottom")

patch 
```



---
## Sparks server update

- 14/23 servers running
  - legacy servers?
- January usage: $AUD: ~80
  - ~30: computing
  - ~20: storage
  - ~15: network traffic
