---
title: "Workreport: RNAcmap &MRFalign"
author: "TC"
date: "2020-05-20"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      chakra: "https://cdnjs.cloudflare.com/ajax/libs/remark/0.14.0/remark.min.js"
      # beforeInit: "https://api.sparks-lab.org/js/sparkscloud.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(ggplot2)
library(patchwork)
load("~/synth_DCA.rda")
```

# RNAcmap paper reviews 

- Overall positive


- Dataset
    - non-redundant RNAs from PDB
    - 800+ more RNAs (expected to finish in 1 week)
    - **Pseudobase++**: 
        - 304 RNAs
    - **RNA atlas**: non-redundant RNAs by species, updated weekly
        - 1874 RNAs
        - length 32~500, single chain
        - 548 RNAs

- Methods to compare
    - Rscape
    - RNAalifold locarna etc

- Standalone package, better documentation etc

---

# MRFalign


- Alignment of 1000 synthetic sequences with defined PK
  - generate 1000 seqs with "((((.AAAA..))))...aaaa..."
  - separately trained MRF and CM models
  - Re-align with MRFalign&CM 
  - DCA of the re-generated MSA

---
# Signal on the MRFalign MSA better

```{r echo=FALSE, fig.width=12}
gg1+ggtitle("Contactmap on MRFalign MSA")+
  gg2+ggtitle("Contactmap on CMalign MSA")

```



