---
title: "Workreport: MRFalign"
author: "TC"
date: "2020-05-20"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      chakra: "https://cdnjs.cloudflare.com/ajax/libs/remark/0.14.0/remark.min.js"
      # beforeInit: "https://api.sparks-lab.org/js/sparkscloud.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.align='center',fig.height = 6,fig.width = 9)
load("~/df.rslt")
library(ggplot2)
library(patchwork)

load("~/ggsparsefull_mrffull.rda")
gg3=gg1
gg4=gg2
```


## Sparse MRF model

- Only keep pairs defined in reference SS

- Double DP for initial seed alignment: works on synthetic MSA but still too slow for real RNAs

---

## MRF_Sparse performs  worse than dense


```{r}

df.rslt$time=c("2mins","17mins")

knitr::kable(df.rslt,format = "html",digits = 2)
```


---

## Pairwise energy inconsistent between mrf_full and mrf_sparse

- Compared to reference alignment and mrf_full alignment: mrf_sparse alignment is favored

```{r}
load("~/ggsparsefull.rda")
gg1=gg1+ggtitle("MRF_sparse")
gg3=gg3+ggtitle("MRF_full")

(gg1+gg2)/(gg3+gg4)
```



---
# Synthetic MSA: MRF_sparse performs better

```{r}
load("~/rslt.synth.rda")

knitr::kable(rslt.synth$df,format = "html",digits = 3)
```


```{r,fig.height=5}
rslt.synth$gg1+rslt.synth$gg2
```

---

## Double DP initialization

```{r}

```


