---
title: "Workreport: MRFalign"
author: "TC"
date: "2020-05-20"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      chakra: "https://cdnjs.cloudflare.com/ajax/libs/remark/0.14.0/remark.min.js"
      # beforeInit: "https://api.sparks-lab.org/js/sparkscloud.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.align='center',fig.height = 6,fig.width = 9)
library(patchwork)
load("~/GIT/HMMtest/rdata/gglist.rda")
```

## RFAM Pseudoknot family re-align

- 58 RFAM families with covariance observed in the PK region.

- Re-align with MRFalign and cmalign

- The alignment quality is measured by comparing the alignment MSA with the seed alignment.

---
## Alignment accuracy

```{r }
gglist$overview
```


---
## PK region

```{r}
gglist$PK
```

---
## Non-PK stem regions
```{r}
gglist$nonPK
```

---
## all regions

```{r}
gglist$scatterall
```

---
## Pseudoknot regions

```{r}
gglist$scatterPK
```


---
## Example1

~50% Pseudoknot base pairs are wrong by CMalign, resulting in bad DCA contacts

```{r}
gglist$exp1 |gglist$exp1_2
```


---
## Example2

```{r}
gglist$exp2 |gglist$exp2_2
```

---
## Same as the artificial PK example

```{r}
library(ggplot2)
load("~/synth_DCA.rda")
gg1+ggtitle("Contactmap on MRFalign MSA")+
  gg2+ggtitle("Contactmap on CMalign MSA")

```



---
## Summary

- MRF align Pseudoknot RNAs better than CMalign given sufficient RNAs(arbitrarily picked 50 for now)
    - CMalign only perform good in cases where Pseudoknots are highly conserved
    - But only 2 good examples (too few?)
    
- Time scales at n(L^4), L>300nt, 100 seqs takes ~6 hours.
    - Probably OK, **95%** RFAM families are under 300nt.
    







